AbxD01 Analysis

### 2015-02-03 abxD01_analysis.Rmd
updated rmd html

---
title: "AbxD01 Analysis"
author: "Alyx Schubert"
date: "September 29, 2014"
output: word_document
---

@@

```{r, eval=FALSE}
file<-read.csv("~/Documents/Github/abxD01/Figure 3/abxD01.final.tx.2.subsample.allstreptitr.forlogscale.csv", header=T)
file<-file[file$expgroup!="1untrStrep",]
kruskal.test(file$Otu001 ~ file$expgroup)
kruskal.test(file$Otu003 ~ file$expgroup)
kruskal.test(file$Otu002 ~ file$expgroup)
kruskal.test(file$Otu005 ~ file$expgroup)
kruskal.test(file$Otu004 ~ file$expgroup)
kruskal.test(file$Otu014 ~ file$expgroup)
kruskal.test(file$Otu006 ~ file$expgroup)
kruskal.test(file$Otu007 ~ file$expgroup)
kruskal.test(file$Otu009 ~ file$expgroup)
kruskal.test(file$Otu015 ~ file$expgroup)
kruskal.test(file$Otu017 ~ file$expgroup)
kruskal.test(file$Other ~ file$expgroup)

@@

@@

Then in r: 
```{r, eval=TRUE}
topdose_logtrans<-read.csv("~/Desktop/mothur/abxD01/rf/abxD01.final.an.unique_list.0.03.subsample.0.03.shared.rf.topdose2.regression.logtrans.filter16mintot.filter16mintot.csv", header=T)
training_logtrans<-topdose_logtrans[,-1]
newtit_logtrans<-read.csv("~/Desktop/mothur/abxD01/rf/abxD01.final.an.unique_list.0.03.subsample.0.03.pick.shared.rf.newtitration.regression.logtrans.filter16mintot.csv", header=T)
testing_logtrans<-newtit_logtrans[,-1] #new titration data only
delay_logtrans<-read.csv("~/Desktop/mothur/abxD01/rf/abxD01.final.an.unique_list.0.03.subsample.0.03.pick.shared.rf.delays.regression.logtrans.csv", header=T)
testing2_logtrans<-delay_logtrans[,-1]

>>>>

---
title: "AbxD01 Analysis"
author: "Alyx Schubert"
date: "September 29, 2014"
output: html_document
---

@@

For comparison of the CFU's among titration groups: 
```{r, eval=TRUE}
file<-read.csv("~/Documents/Github/abxD01/Figure 3/abxD01.final.tx.2.subsample.allstreptitr.forlogscale.csv", header=T)
file<-file[file$expgroup!="1untrStrep",]
avgCD<-tapply(file$nextDayCFU, file$expgroup, mean)
strep_avgCD<-format(avgCD, scientific=TRUE, digits=2)
file$nextDayCFU <- log10(file$nextDayCFU+1)
#kruskal.test(file$nextDayCFU ~ file$expgroup)
# p < 0.0001
#strep_CFU_wilcox <- pairwise.wilcox.test(file$nextDayCFU, file$expgroup, p.adj="BH")
# all significantly different
strep.aov<-aov(file$nextDayCFU ~ file$expgroup)
anova(strep.aov)
#TukeyHSD(strep.aov)
strep_ttest <- pairwise.t.test(file$nextDayCFU, file$expgroup, p.adjust="BH")
print(strep_ttest)
# all significantly different

file<-read.csv("~/Documents/Github/abxD01/Figure 3/abxD01.final.tx.2.subsample.allceftitr.forlogscale.csv", header=T)
file<-file[file$expgroup!="1untrCef",]
avgCD<-tapply(file$nextDayCFU, file$expgroup, mean)
cef_avgCD<-format(avgCD, scientific=TRUE, digits=2)
file$nextDayCFU <- log10(file$nextDayCFU+1)
#kruskal.test(file$nextDayCFU ~ file$expgroup)
# p = 0.003
#cef_CFU_wilcox <- pairwise.wilcox.test(file$nextDayCFU, file$expgroup, p.adj="BH")
# mid and low dose not different, but high different than mid and low
cef.aov<-aov(file$nextDayCFU ~ file$expgroup)
anova(cef.aov)
#TukeyHSD(cef.aov)
cef_ttest <- pairwise.t.test(file$nextDayCFU, file$expgroup, p.adjust="BH")
print(cef_ttest)
# all significantly different

file<-read.csv("~/Documents/Github/abxD01/Figure 3/abxD01.final.tx.2.subsample.allvanctitr.forlogscale.csv", header=T)
file<-file[file$expgroup!="1untrVanc",]
avgCD<-tapply(file$nextDayCFU, file$expgroup, mean)
vanc_avgCD<-format(avgCD, scientific=TRUE, digits=2)
file$nextDayCFU <- log10(file$nextDayCFU+1)
#kruskal.test(file$nextDayCFU ~ file$expgroup)
# p = 0.0016
#vanc_CFU_wilcox <- pairwise.wilcox.test(file$nextDayCFU, file$expgroup, p.adj="BH")
# mid and low dose not different, but high different than mid and low
vanc.aov<-aov(file$nextDayCFU ~ file$expgroup)
anova(vanc.aov)
#TukeyHSD(vanc.aov)
vanc_ttest <- pairwise.t.test(file$nextDayCFU, file$expgroup, p.adjust="BH")
print(vanc_ttest)
# mid and low dose not different, but high different than mid and low

For comparisons between family-level phylotypes:
Performed inside abxD01.barcharts.xOTU.test.r
```{r, eval=FALSE}
file<-read.csv("~/Documents/Github/abxD01/Figure 3/abxD01.final.tx.2.subsample.allstreptitr.forlogscale.csv", header=T)
file<-file[file$expgroup!="1untrStrep",]
kruskal.test(file$Otu001 ~ file$expgroup)
kruskal.test(file$Otu003 ~ file$expgroup)
kruskal.test(file$Otu002 ~ file$expgroup)
kruskal.test(file$Otu005 ~ file$expgroup)
kruskal.test(file$Otu004 ~ file$expgroup)
kruskal.test(file$Otu014 ~ file$expgroup)
kruskal.test(file$Otu006 ~ file$expgroup)
kruskal.test(file$Otu007 ~ file$expgroup)
kruskal.test(file$Otu009 ~ file$expgroup)
kruskal.test(file$Otu015 ~ file$expgroup)
kruskal.test(file$Otu017 ~ file$expgroup)
kruskal.test(file$Other ~ file$expgroup)

@@

Statistical comparison of delayed and on time CFU results:
```{r, eval=TRUE}
file<-read.csv("~/Documents/Github/abxD01/Figure 5/abxD01.final.tx.2.subsample.allmetro.forlogscale.fig5.csv", header=T)
file<-file[file$expgroup!="1untr",]
avgCD<-tapply(file$nextDayCFU, file$expgroup, mean)
metro_avgCD<-format(avgCD, scientific=TRUE, digits=2)
file$nextDayCFU <- log10(file$nextDayCFU+1)
#kruskal.test(file$nextDayCFU ~ file$expgroup)
# p < 0.0001
#strep_CFU_wilcox <- pairwise.wilcox.test(file$nextDayCFU, file$expgroup, p.adj="BH")
# all significantly different
metro.aov<-aov(file$nextDayCFU ~ file$expgroup)
anova(metro.aov)
#TukeyHSD(strep.aov)
metro_ttest <- t.test(file$nextDayCFU~file$expgroup)
print(metro_ttest)
# both significantly different
```

@@

Then in r: 
```{r, eval=FALSE}
topdose_logtrans<-read.csv("~/Desktop/mothur/abxD01/rf/abxD01.final.an.unique_list.0.03.subsample.0.03.shared.rf.topdose2.regression.logtrans.filter16mintot.filter16mintot.csv", header=T)
training_logtrans<-topdose_logtrans[,-1]
newtit_logtrans<-read.csv("~/Desktop/mothur/abxD01/rf/abxD01.final.an.unique_list.0.03.subsample.0.03.pick.shared.rf.newtitration.regression.logtrans.filter16mintot.csv", header=T)
testing_logtrans<-newtit_logtrans[,-1] #new titration data only
delay_logtrans<-read.csv("~/Desktop/mothur/abxD01/rf/abxD01.final.an.unique_list.0.03.subsample.0.03.pick.shared.rf.delays.regression.logtrans.csv", header=T)
testing2_logtrans<-delay_logtrans[,-1]
